%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
% Modified by:
% Ritik Raina - 02/01/2020
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[sfdefault]{universalis}
\usepackage[left=0.4in,top=0.2in,right=0.4in,bottom=0.2in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage[dvipsnames]{xcolor}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ritik Raina} % Your name
\address{ \faHome{ San Diego, CA } \faPhone{  (818)~629-7022 } 
\href{https://www.ritik.xyz}{\faDesktop}{ 
\href{https://www.ritik.xyz}{ritik.xyz} } 
\href{https://www.linkedin.com/in/ritikraina/}{\faLinkedin}{ \href{https://www.linkedin.com/in/ritikraina/}{ritikraina} }  
\faEnvelope{ \href{mailto:rraina@ucsd.edu}{rraina@ucsd.edu} } \faGithub{  \href{https://github.com/rainarit}{rainarit} }} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
 % Your phone number and email
%\address{www.linkedin.com/in/kylegillaspy}

\begin{document}
%{\fontfamily{lmss}\selectfont
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%\begin{rSection}{\faBook{ }}{Objective}
%Passionate and energetic individual seeking to join as a Software Engineering / Data Science %Intern to contribute and deliver quality software solutions by applying interpersonal skills %and knowledge of Algorithms, Data Science, and Data Structures.
%\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{\faUniversity{ }}{Education}
\begin{rSubsection}{}
{\bf University of California, San Diego} {\em September 2018 - \bf{June 2022}} 
{B.S. Cognitive Science: Specialization in Machine Learning and Neural Computation} {}
%\\ \textbf{Business Courses:}
%\\Financial \& Managerial Accounting, Managing Diverse Teams, Project Management, Financial Analysis
%\\ \textbf{ACT: 36} | English-35 Math-36 Reading-36 Science-36 Essay-12/12
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{\faBook{ }}{Relevant Coursework}
\itab{Advanced Data Structures} \tab{}  \tab{Algorithms and Systems Analysis} 
\\ \itab{Data Science in Practice} \tab{}  \tab{Computer Organization and Systems Programming} 
\\ \itab{Object Oriented Programming} \tab{} \tab{Artificial Intelligence Algorithms}
%\ \itab{Financial \& Managerial Accounting} \tab{}  \tab{Management of Diverse Teams}
\end{rSection}
%--------------------------------------
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\faLaptop{ }}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages &  Java, Python, Swift, React.js, HTML, CSS, C++, LaTeX, Bash, Assembly \\
Software \& Tools & UNIX, Git, Vim, Jupyter, MongoDB, CocoaPods, Google Firebase, OpenCV, OpenGL, Tensorflow
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{\faCode{ }}{Experience \& Leadership}

\begin{rSubsection}{}{CodePath | {\normalfont Technical Program Manager}}{January 2020 - Present}{}{San Diego, CA}{\it \textbf{Worked with:} Xcode 11, Swift, CocoaPods }
\item Increased the largest pipeline of high-performing underrepresented engineers in tech via
Codepath, a nonprofit that has raised \$1 million from Facebook.
\item Taught a Facebook-designed 12-week iOS course to 45+ students via hands-on experience on Swift, Xcode, and Git.
\item As an instructor, I was required to maintain a high-level of understanding of the curriculum topics including but not limited to: Frameworks, iOS Libraries, Back-end (Parse), APIs, AutoLayout (constraints), and CocoaPods.
\end{rSubsection}

\begin{rSubsection}{}{STAR Capital | {\normalfont Machine Learning Intern}}{July 2019 - September 2019}{}{Jakarta, Indonesia}{\it \textbf{Worked with:} Python, Tensorflow, OpenCV, Dlib C++, Firebase, SciPy, NumPy, Pandas, Keras}
\item Developed Python scripts which used Selenium, Request, and BeautifulSoup frameworks for evaluating web-scraping models. These models were then used to scrape credit rating documents off FinTech sites.
\item Researched and developed spatial models for training and evaluating facial detection \& recognition systems based on employee data. 
\item Designed	and	implemented custom spatial algorithms and data structures for deriving facial landmarks.
\end{rSubsection}

\begin{rSubsection}{}{VennPool | {\normalfont Software Developer}}{November 2018 - April 2019}{}{San Diego, CA}{\it \textbf{Worked with:} HTML/CSS/JavaScript, Bootstrap, Firebase, Expo, React}
\item Designed and developed the company website’s interface using Bootstrap themes and CSS/Semantic UI.
\item Communicated with mentors and investors as a part of the startup incubator, The Basement.
\item Worked with Google Firebase APIs to authorize access to the application and control service operation access.
\end{rSubsection}

\end{rSection}

\begin{rSection}{\faDatabase{ }}{Research} 

\begin{rSubsection}{}{\href{https://www.mattarlab.com/page}{Mattar Lab} | {\normalfont Research Assistant}}{April 2020 - Present}{\it \textbf{Worked with:} JavaScript, jsPsych, Python, RL}{}
\item Under the guidance of \href{http://marcelomattar.com/}{Prof. Marcelo Mattar}
\item Developed computational models using Reinforcement Learning and Bayesian Interface that would predict decisions and the processes underlying it via the game of Chess.
\item Grounded these models in behavioral and neuroscientific data from decision-making experiments, conducted either in our lab (human behavior and neuroimaging) or with collaborators (animal electrophysiology)

\end{rSubsection}
\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{\faDatabase{ }}{Projects} 

\begin{rSubsection}{}{\href{https://github.com/rainarit/invoice-logger}{Invoice Logger}}{January 2020}{\textbf{Uses:} MongoDB, Express, HTML/CSS/JavaScript, React}{}
\item Built	a reactive web application using MERN stack for querying banking transactions uploaded to a MongoDB collection. Built to explore the various features of MongoDB Atlas.
\end{rSubsection}
\begin{rSubsection}{}{\href{https://github.com/rainarit/tweet4me}{Tweet4Me}}{December 2019}{\textbf{Uses:} Swift, Alamofire, Twitter REST API, UIKit, AFNetworking}{}
\item Custom Twitter app for browsing and interacting with a personalized feed.
\item Implements the Twitter RESTful API to supply feed with tweets and allow users to tweet, retweet, and favorite.
\end{rSubsection}
\begin{rSubsection}{}{\href{https://github.com/rainarit/SDHacks2019_Awakened}{Awakened: Eye Predictor for User Vehicle Safety}}{October 2019}{\textbf{Uses: } Python, SciPy Spatial, Dlib, iMutils  }{}
\item A Python/Django application which could monitor the eyes of a driver. If the driver's eyes were closed for $\geq$2 seconds, an alert would buzz to wake the driver. After each vehicle trip, an online report would be made to measure the total time the driver was unconscious for. This was a group project built at the 2019 MLH SDHacks.
\end{rSubsection}
\end{rSection}
% EXTRA STUFF


%-------------------------------------------------------------

\end{document}
